---
title: "Alcohol vs Seat choice"
author: "Alondra Garcia"
date: "June 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.   
$H_A$: The average number drinks is different between at least two rows.

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
In the chart the middle point represents the median of the group of people. It is the highest number from either one of the other groups. The back row is about 50% of the people. The Front row has the least percentage. According to the chart the people in the back are consuming the most alcohol. 
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The variability in the back row is bigger than the variability of the front and back row.

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```
According to the chart, the back row average is 9.6 which is much bigger from the average of the front or middle row. The majority of the people are sitting in the middle section.

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

```{r}
plot(TukeyHSD(model1))
```

There is a difference

## Conclusions


